On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-07-23 docs/mvfits_paper/mvf.tex
completing gmvr topy problem section ... for now

\tbl{tb:gmvrtoy} demonstrates \gmvr{}'s accurate recovery of the underlying model parameters. We note that that in going from \gmvr{}'s initial output contains terms in the numerator which correspond to the addition of a constant to the overall model, thus correcting for the difference between the offset parameter, $\mu$, and the true, but arbitrary, mean of the dataset.

@@

\end{table}
%
%
\par Here, it is clear that \gmvr{} correctly recovers the functional form of the input data. In general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
%
However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
%
In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
%
%
\begin{figure*}
  %
  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
  %
	\caption{ Standard summary plot for \gmvr. }
  %
  \label{fig:gmvrtoy}
  %
\end{figure*}

>>>>

\tbl{tb:gmvrtoy} demonstrates \gmvr{}'s accurate recovery of the underlying model parameters.
We note that \gmvr{}'s initial output contains terms in the numerator which correspond to the addition of a constant to the overall model, thus correcting for the difference between the offset parameter, $\mu$, and the true, but arbitrary, mean of the dataset.
\tbl{tb:gmvrtoy} presents recovered model parameters after this effect has been accounted for with simple algebraic manipulation.

@@

\end{table}
%
%
\par In this example case, \gmvr{} correctly recovers the functional form of the input data. But, in general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
%
However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
%
In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
%
%
\begin{figure*}
  %
  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
  %
	\caption{ Standard summary plot for \gmvr. }
  %
  \label{fig:gmvrtoy}
  %
\end{figure*}
